\documentclass[thesis]{thesis-umich}


%%%% THE FOLLOWING PACKAGE IS FOR TEST USE ONLY %%%%
%%%% PLEASE DELETE %%%%
%%%% PLEASE DELETE %%%%
%%%% PLEASE DELETE %%%%
\usepackage{kantlipsum}
%%%%

% includeonly controls partial output (only chapters included are built)
\includeonly{chap1,chap2,appendix1}

\title{\LaTeX~Template for Rackham Dissertations}

% Author name
\author{Jane R. Doe}
\authoremail{jdoe@umich.edu}
\orcidid{9999-9999-9999-9999}

% Department
\department{Physics}

% Year of completion
\year=2022

% Committee members
\committee{
  Professor John D. Brown, Co-Chair,\\
  Professor Emeritus Ann A. Smith, Co-Chair\\
  Dr. Alicia Gonzalez, Mellon Foundation\\
  Assistant Professor Charles Z. Jones\\
  Associate Professor Kathleen X. Lee, Yale University\\
  Associate Professor Horace H. Rackham
}

% For each command below, if the page is not needed, comment out the whole command
% number in the square bracket specifies the foramt of the title.
% Style 2: simple bold italic heading
% Style 3: Spread caps heading
% Style 4: 2022 ver. simple bold, no italics
\dedication[4]{
  This manual is dedicated to all doctoral students at the University of
  Michigan's Horace H. Rackham School of Graduate Studies.
}

\acknowledgments[4]{
  This template has been modified by a lot of people over the years. To the best of my knowledge, its original version was written by Jin Ji in 1988. Modifications to it have since been made by Roque D.\ Oliveira in 1992, Jason Gilbert  in 2008, Derek Dalle in 2011, and Umang Varma in 2019. It is possible that other people have modified this document (in fact, there is an unattributed change in the changelog dated 1989.11.29).
}

\preface[4]{
  This is a joint work of several people.
}

\foreword[4]{
  This dissertation is a sample document using the \texttt{thesis-umich.cls}
  template.
}

\prologue[4]{
  Feel free to write your own masterpiece.
}
% End For


% Commands to hide or show copyright, lists of figures, tables, etc.
\showcopyright
\showlistoffigures
\showlistoftables
%\showlistofmaps
%\showlistofillustrations
\showlistofappendices
\showlistofabbreviations
%\showlistofacronyms % Build errors can occur if an empty list is turned on
%\showlistofsymbos

\usereferencesperchapter

% Definition of any abbreviations used.
\abbreviations{
 \acro{ABBREV1}{abbreviation 1}
 \acro{ABBREV2}{abbreviation 2}
}

% Some abstract text
\abstract{
  With walk through basic steps of using this \LaTeX~template.
}

% Codes to generate chapters in roman numerals while keep (sub-)section
% in arabic numerals.
% For example, the following code will generate
%    Chapter I
%        Section 1.1
\renewcommand{\thechapter}{\arabic{chapter}} %
%\renewcommand{\thechapter}{\Roman{chapter}} %
\renewcommand{\thesection}{\arabic{chapter}.\arabic{section}} %
\renewcommand{\thesubsection}{\arabic{chapter}.\arabic{section}.\arabic{subsection}} %%

\begin{document}
\include{chap1}
\include{chap2}
\include{chap3}

\appendix
\include{appendix1}

\end{document}
